First steps in synthetic algebraic geometry

### 2017-03-20 snippets/qcoh.tex
Internal construction of the relative spectrum
Integrated the section on the relative spectrum construction in the big Zariski topos

By Proposition~\ref{XXX}, the internal expression~$\Spec(A)$ is the functor of
points of~$\RelSpek_S \A_0$. For any~$S$-scheme~$f : T \to S$ contained in the site
used to define~$\Zar(S)$, we consider the fiber product
\[ \xymatrix{
  \RelSpek_T(f^*\A_0) \ar[r]^{f'} \ar[d]_{p'} & \RelSpek_S\A_0 \ar[d]^p \\
  T \ar[r]_f & S.
} \]
Since~$\RelSpek_T(f^*\A_0) \to S$ is contained in the site (for any of our
admissible sites), we may conclude using the following chain of isomorphisms:
\begin{align*}
  [\Spec(A), E](T) &\cong
  \Hom_{\Zar(S)}(\ul{T}, [\Spec(A), E])
  \cong \Hom_{\Zar(S)}(\ul{T} \times \Spec(A), E) \\
  &\cong \Hom_{\Zar(S)}(\underline{T \times_S \RelSpek_S\A_0}, E)
  \cong E(\RelSpek_T(f^*\A_0)) \\
  &\cong \Gamma(\RelSpek_T(f^*\A_0), (p')^* f^* \E_0)
  \cong \Gamma(T, (p')_* (p')^* f_* \E_0) \\
  &\cong \Gamma(T, f^*\E_0 \otimes_{\O_T} f^*\A_0)
  \cong \Gamma(T, (\E_0 \otimes_{\O_S} \A_0)^\Zar) \\
  &\cong \Gamma(T, (\E_0)^\Zar \otimes_\affl (\A_0)^\Zar)
  \cong \Gamma(T, E \otimes_\affl A).
\end{align*}
The antepenultimate isomorphism is because pullback of modules in~$\Sh(S)$ to
modules in~$\Sh(T)$ commutes with tensor product. The penultimate isomorphism
is because pullback of a sheaf in~$\Sh(S)$ to a sheaf in~$\Zar(S)$ commutes
with tensor product (Lemma~\ref{lemma:zar-tensor-product-commutes}).

@@

\begin{rem}The condition in Scholium~\ref{scholium} that~$\Spec(A)$ is
representable by an object of the site used to define~$\Zar(S)$ is slightly
unnatural from a topos-theoretic point of view, since the conclusion of the
Scholium depends only on the topos over the site and not the site itself.
In fact, the condition can be weakened and made more natural at the
same time: It suffices to require that~$\Spec(A)$ is \emph{locally}
representable by an object of the site.

>>>>

By Proposition~\ref{prop:relative-spectrum-big-zariski}, the internal expression~$\Spec(A)$ is the functor of
points of~$\RelSpek_S \A_0$. For any~$S$-scheme~$f : T \to S$ contained in the site
used to define~$\Zar(S)$, we consider the fiber product
\[ \xymatrix{
  \RelSpek_T(f^*\A_0) \ar[r]^{f'} \ar[d]_{p'} & \RelSpek_S\A_0 \ar[d]^p \\
  T \ar[r]_f & S.
} \]
Since~$\RelSpek_T(f^*\A_0) \to S$ is contained in the site (for any of our
admissible sites), we may conclude using the following chain of isomorphisms:
\begin{align*}
  [\Spec(A), E](T) &\cong
  \Hom_{\Zar(S)}(\ul{T}, [\Spec(A), E])
  \cong \Hom_{\Zar(S)}(\ul{T} \times \Spec(A), E) \\
  &\cong \Hom_{\Zar(S)}(\underline{T \times_S \RelSpek_S\A_0}, E)
  \cong E(\RelSpek_T(f^*\A_0)) \\
  &\cong \Gamma(\RelSpek_T(f^*\A_0), (p')^* f^* \E_0)
  \cong \Gamma(T, (p')_* (p')^* f_* \E_0) \\
  &\cong \Gamma(T, f^*\E_0 \otimes_{\O_T} f^*\A_0)
  \cong \Gamma(T, (\E_0 \otimes_{\O_S} \A_0)^\Zar) \\
  &\cong \Gamma(T, (\E_0)^\Zar \otimes_\affl (\A_0)^\Zar)
  \cong \Gamma(T, E \otimes_\affl A).
\end{align*}
The antepenultimate isomorphism is because pullback of modules in~$\Sh(S)$ to
modules in~$\Sh(T)$ commutes with tensor product. The penultimate isomorphism
is because pullback of a sheaf in~$\Sh(S)$ to a sheaf in~$\Zar(S)$ commutes
with tensor product (Lemma~\ref{lemma:zar-tensor-product-commutes}).

@@

\begin{rem}\label{rem:local-representability}
The condition in Scholium~\ref{scholium} that~$\Spec(A)$ is
representable by an object of the site used to define~$\Zar(S)$ is slightly
unnatural from a topos-theoretic point of view, since the conclusion of the
Scholium depends only on the topos over the site and not the site itself.
In fact, the condition can be weakened and made more natural at the
same time: It suffices to require that~$\Spec(A)$ is \emph{locally}
representable by an object of the site.
